Download data

### 2024-05-07 scripts/subsetDataforCrews.Rmd
fn

lapply(teams_list[13], project_maker,
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)

lapply(seniors_list[3],  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
      # historic_SOS, 
       roads = roads, seed_transfer = STZ)

>>>>

ob <- lapply(teams_list[13], project_maker,
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)

plot( ab[["Uncompahgre - P102085"]][["Astragalus lonchocarpus"]] )

lapply(seniors_list[3],  project_maker,
       admu = admin_boundaries, intype = 'senior',
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, seed_transfer = STZ)
